### 2024-08-27 paper.tex
different proof of change of basis.  not sure if better or not.

\begin{lemma}
    \(\mathcal{P} = \bigcup_{1 \leq w \leq k, 0 \leq r \leq \lambda_{w}} \mathcal{P}_{wr}\).
\end{lemma}
\begin{proof}
    Let \((A_{a, b}, (V_i)) \in \mathcal{P}\).
    Define \(f : \mathbb{C}^m \to \mathbb{C}\) by \(f(e_{ij}) = a_{ij}\).
    Since \(A_{a, b}\) is nilpotent, \cref{normalization} says that there is a change of basis \(P\) such that \(P^{-1}XP = X\), and for all but one pair \((i, j)\) we have \(f(Pe_{ij}) = 0\).
    Since \(P^{-1}XP = X\), it is easy to see (writing out the matrix multiplication, if necessary) that there are \(a',b'\) such that \((P^{-1}, I_n)A_{a,b}(P, I_n) = A_{a',b'}\).
    \par Now,
    \begin{align*}
        P^{-1}XPe_{ij} + f(Pe_{ij}) f_n & = \\
        (P^{-1}, I_n)A_{a,b}(P, I_n)(e_{ij}, 0) & = \\
        A_{a'b'} (e_{ij},0) & = \\
        Xe_{ij} + a'_{ij} f_n & .
    \end{align*}
    Thus we see that \(a'_{ij} = 0\) for all pairs \((i,j)\) except one; or in other words, \(A_{a'b'}\) is of the form \(A_{e_{wr}b'}\).
\end{proof}
\begin{lemma}
    \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\) exactly when either \(r_1 = r_2 = 0\), or \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\).
    When \(\mathcal{P}_{w_1r_1} \neq \mathcal{P}_{w_2r_2}\), we have \(\mathcal{P}_{w_1r_1} \cap \mathcal{P}_{w_2r_2} = \emptyset\). 
\end{lemma}
\begin{proof}
    Now, if \(r_1 = r_2 = 0\), we have \(e_{wr_1} = e_{wr_2} = 0\), so clearly \(\mathcal{P}_{wr_1} = \mathcal{P}_{wr_2}\).
    And if \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\), then clearly any matrix of the form \(A_{e_{w_1r_1}b'}\) can be transformed to a matrix of the form \(A_{e_{w_2r_2}b'}\) by making the change of basis that swaps \(e_{w_1j}\) with \(e_{w_2j}\).
    Inversely, suppose

>>>>

\begin{lemma}
    \(\mathcal{P} = \bigcup_{1 \leq w \leq k, 0 \leq r \leq \lambda_{w}} \mathcal{P}_{wr}\).
\end{lemma}
\begin{proof}
    Let \((A_{a, b}, (V_i)) \in \mathcal{P}\).
    Define \(f : \mathbb{C}^m \to \mathbb{C}\) by \(f(e_{ij}) = a_{ij}\).
    We take the coordinate-free view of \(A_{a,b}\) as the linear transformation \(T\) that sends \(e_{ij}\) to \(e_{i,j - 1} + f(e_{ij})\), sends \(f_{i + 1}\) to \(f_i\), and sends \(f_1\) to \((b, 0)\).
    Since \(X\) is nilpotent, \cref{normalization} says that there is a change of basis \(P\) such that \(Pe_{ij}\) forms a Jordan basis for \(X\), and for all but one pair \((i, j)\) we have \(f(Pe_{ij}) = 0\).
    \par Because \(Pe_{ij}\) is a Jordan basis, \(A_{a',b'}\) of \(T\) in this new basis has the same upper-left corner \(X\); and since \(f(Pe_{ij}) = 0\) for all but one pair \((i,j)\), we have \(a'_{ij} = 0\) for all but one pair \((i,j)\).
\end{proof}
\begin{lemma}
    \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\) exactly when either \(r_1 = r_2 = 0\), or \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\).
    When \(\mathcal{P}_{w_1r_1} \neq \mathcal{P}_{w_2r_2}\), we have \(\mathcal{P}_{w_1r_1} \cap \mathcal{P}_{w_2r_2} = \emptyset\). 
\end{lemma}
\begin{proof}
    Now, if \(r_1 = r_2 = 0\), we have \(e_{wr_1} = e_{wr_2} = 0\), so clearly \(\mathcal{P}_{wr_1} = \mathcal{P}_{wr_2}\).
    And if \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\), then clearly any matrix of the form \(A_{e_{w_1r_1}b'}\) can be transformed to a matrix of the form \(A_{e_{w_2r_2}b'}\) by making the change of basis that swaps \(e_{w_1j}\) with \(e_{w_2j}\).
    Conversely, suppose \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\).
    Then there is \(P\) such that \((P^{-1},I_n) A_{e_{w_1r_1},b} (P, I_n) = A_{e_{w_2r_2}, b'}\).

    Then, either there is \(k\) such that (for any \(b_1',b_2'\)) \(A_{e_{w_1r_1}b_1'}^k \)
    \par The second observation, that the nonequal sets are disjoint, just follows from the fact that (this restricted form of) similarity is an equivalence relation.
\end{proof}
